---
title: "HG on and off Track"
author: "Anna Talucci"
date: '2023-01-07'
output: html_document
---

# Overview
Here we explore the off and on track data for the water track at Howard Glacier. 


# Packages
```{r}
library(tidyverse)
library(lubridate)
library(gt)
library(gtsummary)
library(skimr)
library(cowplot)
```

# Data
```{r}
hgoff = read.csv("../data/decagon_data/hg_off/HGOFF2Jan23-1609-all.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

```{r}
hgon = read.csv("../data/decagon_data/hg_on/HG_on_V2Jan23-1602-all.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

# Check data
```{r}
head(hgoff)
```

```{r}
head(hgon)
```

# Clean

## Off track

### Surface data
Rename columns, and convert NAs to NA.
```{r}
surfaceOff1 = hgoff %>% 
  dplyr::rename(datetime = HGOFF, vwc1 = Port.1, temp1 = Port.1.1, ec1 = Port.1.2,vwc2 = Port.2, temp2 = Port.2.1, ec2 = Port.2.2, vwc3 = Port.3, temp3 = Port.3.1, ec3 = Port.3.2, vwc4 = Port.4, temp4 = Port.4.1, ec4 = Port.4.2, rh=Port.5, airtemp = Port.5.1) %>%
   mutate(across(where(is.character), ~na_if(., "#N/A")))
```

#### Remove first 2 rows
```{r}
surfaceOff1 <- surfaceOff1[-c(1:2),]
```

```{r}
surfaceOff1
```

#### Select air temperature and relative humidity

```{r}
surfaceOff2 = surfaceOff1 %>% 
  dplyr::select(datetime, rh, airtemp) %>% 
  drop_na(.) %>% 
  type_convert() %>%
  tidyr::separate(., datetime, c("date", "time", "ampm"), sep = " ") %>%
  mutate(rh=rh*100) 
```
```{r}
str(surfaceOff2)
```

```{r}
surfaceOff2
```
#### Remove the fisrt 2 rows with wierd values
```{r}
surfaceOff2 <- surfaceOff2[-c(1:2),]
```


#### Covert to date
```{r}
surfaceOff2$date <- lubridate::mdy(surfaceOff2$date)
```

```{r}
surfaceOff2
```

### Subsurface data
Rename columns, and convert NAs to NA.
```{r}
subOff1 = hgoff %>% 
  dplyr::rename(datetime = HGOFF, vwc1 = Port.1, temp1 = Port.1.1, ec1 = Port.1.2,vwc2 = Port.2, temp2 = Port.2.1, ec2 = Port.2.2, vwc3 = Port.3, temp3 = Port.3.1, ec3 = Port.3.2, vwc4 = Port.4, temp4 = Port.4.1, ec4 = Port.4.2, rh=Port.5, airtemp = Port.5.1) %>%
   mutate(across(where(is.character), ~na_if(., "#N/A")))

subOff1
```

#### Remove first 2 rows
```{r}
subOff1 <- subOff1[-c(1:2),]
```


#### Select subsurface variables

```{r}
subOff2 = subOff1 %>% 
  dplyr::select(datetime, vwc1:ec4) %>% 
  drop_na(.) %>% 
  type_convert() %>%
  tidyr::separate(., datetime, c("date", "time", "ampm"), sep = " ")
```

```{r}
str(subOff2)
```

```{r}
subOff2
```

### Covert to date
```{r}
subOff2$date <- lubridate::mdy(subOff2$date)
```

```{r}
subOff2
```

## On track
```{r}
hgon
```
### Surface data
Rename columns, and convert NAs to NA.
```{r}
surfaceOn1 = hgon %>% 
  dplyr::rename(datetime = HG_on_V, vwc1 = Port.1, temp1 = Port.1.1, ec1 = Port.1.2,vwc2 = Port.2, temp2 = Port.2.1, ec2 = Port.2.2, vwc3 = Port.3, temp3 = Port.3.1, ec3 = Port.3.2, vwc4 = Port.4, temp4 = Port.4.1, ec4 = Port.4.2, rh=Port.5, airtemp = Port.5.1) %>%
   mutate(across(where(is.character), ~na_if(., "#N/A")))
```

#### Remove first 2 rows
```{r}
surfaceOn1 <- surfaceOn1[-c(1:2),]
```

```{r}
surfaceOn1
```

#### Select air temperature and relative humidity

```{r}
surfaceOn2 = surfaceOn1 %>% 
  dplyr::select(datetime, rh, airtemp) %>% 
  drop_na(.) %>% 
  type_convert() %>%
  tidyr::separate(., datetime, c("date", "time", "ampm"), sep = " ") %>%
  mutate(rh=rh*100) 
```

```{r}
str(surfaceOn2)
```

```{r}
surfaceOn2
```

#### Remove the fisrt 2 rows with wierd values
```{r}
surfaceOn2 <- surfaceOn2[-1,]
```


#### Covert to date
```{r}
surfaceOn2$date <- lubridate::mdy(surfaceOn2$date)
```

```{r}
surfaceOn2
```

### Subsurface data
Rename columns, and convert NAs to NA.
```{r}
subOn1 = hgon %>% 
  dplyr::rename(datetime = HG_on_V, vwc1 = Port.1, temp1 = Port.1.1, ec1 = Port.1.2,vwc2 = Port.2, temp2 = Port.2.1, ec2 = Port.2.2, vwc3 = Port.3, temp3 = Port.3.1, ec3 = Port.3.2, vwc4 = Port.4, temp4 = Port.4.1, ec4 = Port.4.2, rh=Port.5, airtemp = Port.5.1) %>%
   mutate(across(where(is.character), ~na_if(., "#N/A")))

subOn1
```

#### Remove first 2 rows
```{r}
subOn1 <- subOn1[-c(1:2),]
```


#### Select subsurface variables

```{r}
subOn2 = subOn1 %>% 
  dplyr::select(datetime, vwc1:ec4) %>% 
  drop_na(.) %>% 
  type_convert() %>%
  tidyr::separate(., datetime, c("date", "time", "ampm"), sep = " ")
```

```{r}
str(subOn2)
```

```{r}
subOn2
```

### Covert to date
```{r}
subOn2$date <- lubridate::mdy(subOn2$date)
```

```{r}
subOn2
```




# Summary Tables

## Off Track

### Surface off track

```{r}
( t1 = surfaceOff2 %>% 
  dplyr::select(rh, airtemp) %>% 
  tbl_summary(                                     
    type = all_continuous() ~ "continuous2",       
    statistic = all_continuous() ~ c(
      "{mean} ({sd})",                             
      "{median} ({p25}, {p75})",                   
      "{min}, {max}"),                            
    label  = list(rh   ~ "Relative humidity (%)", airtemp ~ "Air Temperature (°C)")) %>%
  as_gt() %>%
  gt::tab_header(title = "Howard glacier off track surface",
                 subtitle = "Summary statistics")
)
```

```{r eval=FALSE, include=FALSE}
gt::gtsave(t1, filename = "../outputs/Tables/HGOffSurface.html")
```

### Subsurface off track

```{r}
( t2 = subOff2 %>% 
  dplyr::select(vwc1, temp1, ec1, vwc2, temp2, ec2, vwc3, temp3, ec3, vwc4, temp4, ec4) %>%                      
  tbl_summary(                                     
    type = all_continuous() ~ "continuous2",       
    statistic = all_continuous() ~ c(
      "{mean} ({sd})",                             
      "{median} ({p25}, {p75})",                   
      "{min}, {max}"),                            
    label  = list(vwc1  ~ "0cm Moisture (m³/m³)", 
                  temp1 ~ "0cm Temperature (°C)", 
                  ec1 ~ "0cm Electrical conductivity (mS/cm)", 
                  vwc2 ~ "10cm Moisture (m³/m³)", 
                  temp2 ~ "10cm Temperature (°C)", 
                  ec2 ~ "10cm Electrical conductivity (mS/cm)", 
                  vwc3 ~ "20cm Moisture (m³/m³)", 
                  temp3 ~ "20cm Temperature (°C)", 
                  ec3 ~ "20cm Electrical conductivity (mS/cm)", 
                  vwc4 ~ "30cm Moisture (m³/m³)", 
                  temp4 ~ "30cm Temperature (°C)", 
                  ec4 ~ "30cm Electrical conductivity (mS/cm)" )) %>%
  as_gt() %>%
  gt::tab_header(title = "Howard glacier off track soil profile",
                 subtitle = "Summary statistics")
)
```

```{r eval=FALSE, include=FALSE}
gt::gtsave(t2, filename = "../outputs/Tables/HGOffSoilProfile.html")
```




## On Track

### Surface 

```{r}
( t3 = surfaceOn2 %>% 
  dplyr::select(rh, airtemp) %>% 
  tbl_summary(                                     
    type = all_continuous() ~ "continuous2",       
    statistic = all_continuous() ~ c(
      "{mean} ({sd})",                             
      "{median} ({p25}, {p75})",                   
      "{min}, {max}"),                            
    label  = list(rh   ~ "Relative humidity (%)", airtemp ~ "Air Temperature (°C)")) %>%
  as_gt() %>%
  gt::tab_header(title = "Howard glacier on track surface",
                 subtitle = "Summary statistics")
)
```

```{r eval=FALSE, include=FALSE}
gt::gtsave(t3, filename = "../outputs/Tables/HGOnSurface.html")
```

### Subsurface off track

```{r}
( t4 = subOn2 %>% 
  dplyr::select(vwc1, temp1, ec1, vwc2, temp2, ec2, vwc3, temp3, ec3, vwc4, temp4, ec4) %>%                      
  tbl_summary(                                     
    type = all_continuous() ~ "continuous2",       
    statistic = all_continuous() ~ c(
      "{mean} ({sd})",                             
      "{median} ({p25}, {p75})",                   
      "{min}, {max}"),                            
    label  = list(vwc1  ~ "0cm Moisture (m³/m³)", 
                  temp1 ~ "0cm Temperature (°C)", 
                  ec1 ~ "0cm Electrical conductivity (mS/cm)", 
                  vwc2 ~ "10cm Moisture (m³/m³)", 
                  temp2 ~ "10cm Temperature (°C)", 
                  ec2 ~ "10cm Electrical conductivity (mS/cm)", 
                  vwc3 ~ "20cm Moisture (m³/m³)", 
                  temp3 ~ "20cm Temperature (°C)", 
                  ec3 ~ "20cm Electrical conductivity (mS/cm)", 
                  vwc4 ~ "30cm Moisture (m³/m³)", 
                  temp4 ~ "30cm Temperature (°C)", 
                  ec4 ~ "30cm Electrical conductivity (mS/cm)" )) %>%
  as_gt() %>%
  gt::tab_header(title = "Howard glacier on track soil profile",
                 subtitle = "Summary statistics")
)
```

```{r eval=FALSE, include=FALSE}
gt::gtsave(t4, filename = "../outputs/Tables/HGOnSoilProfile.html")
```


# Summary dataframes for plots

## Off track
### Surface means
```{r}
meanOffsurface = surfaceOff2 %>% 
  group_by(date) %>%
  summarise(rh_min =min(rh),
            rh_mean = mean(rh),
            rh_max = max(rh),
            temp_min = min(airtemp),
            temp_mean = mean(airtemp),
            temp_max = max(airtemp)) %>%
  dplyr::select(date, rh_mean, temp_mean) %>%
  rename( rh=rh_mean, airtemp=temp_mean)  

meanOffsurface
```

### Subsurface means

```{r}
meanOffsub = subOff2 %>% 
  group_by(date) %>%
  summarise(vwc1_mean =mean(vwc1),
            vwc2_mean =mean(vwc2),
            vwc3_mean =mean(vwc3),
            vwc4_mean =mean(vwc4),
            temp1_mean = mean(temp1),
            temp2_mean = mean(temp2),
            temp3_mean = mean(temp3),
            temp4_mean = mean(temp4),
            ec1_mean = mean(ec1),
            ec2_mean = mean(ec2),
            ec3_mean = mean(ec3),
            ec4_mean = mean(ec4)) %>%
  rename( vwc1=vwc1_mean, 
          vwc2=vwc2_mean,
          vwc3=vwc3_mean,
          vwc4=vwc4_mean,
          temp1=temp1_mean, 
          temp2=temp2_mean,
          temp3=temp3_mean,
          temp4=temp4_mean,
          ec1=ec1_mean, 
          ec2=ec2_mean,
          ec3=ec3_mean,
          ec4=ec4_mean)

meanOffsub
```

## On track
### Surface means
```{r}
meanOnsurface = surfaceOn2 %>% 
  group_by(date) %>%
  summarise(rh_min =min(rh),
            rh_mean = mean(rh),
            rh_max = max(rh),
            temp_min = min(airtemp),
            temp_mean = mean(airtemp),
            temp_max = max(airtemp)) %>%
  dplyr::select(date, rh_mean, temp_mean) %>%
  rename( rh=rh_mean, airtemp=temp_mean) 

meanOnsurface
```

### Subsurface means

```{r}
meanOnsub = subOn2 %>% 
  group_by(date) %>%
  summarise(vwc1_mean =mean(vwc1),
            vwc2_mean =mean(vwc2),
            vwc3_mean =mean(vwc3),
            vwc4_mean =mean(vwc4),
            temp1_mean = mean(temp1),
            temp2_mean = mean(temp2),
            temp3_mean = mean(temp3),
            temp4_mean = mean(temp4),
            ec1_mean = mean(ec1),
            ec2_mean = mean(ec2),
            ec3_mean = mean(ec3),
            ec4_mean = mean(ec4)) %>%
  rename( vwc1=vwc1_mean, 
          vwc2=vwc2_mean,
          vwc3=vwc3_mean,
          vwc4=vwc4_mean,
          temp1=temp1_mean, 
          temp2=temp2_mean,
          temp3=temp3_mean,
          temp4=temp4_mean,
          ec1=ec1_mean, 
          ec2=ec2_mean,
          ec3=ec3_mean,
          ec4=ec4_mean)

meanOnsub
```


# Plot 

## Define graph Theme 
```{r}
theme_reg = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.3), "cm")) +
  theme(axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9, hjust = 0.5, vjust = 0.5),
        axis.text.x = element_text(size = 7, color = "black"),
        axis.text.y = element_text(size = 7, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))
```

```{r}
theme_legend = theme_bw() + theme(legend.position = "bottom") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black")) +
  theme(legend.title = element_blank())   
```

## Define Labels
```{r}
ecUnits = "Electrocal conductivity\n(mS/cm)" 
vwcUnits = "Moisture\n(m³/m³)" 
tempUnits =  "Temperature\n(°C)"
tempLab <- "Temperature (°C)"
rhLab = "Relative humidity (%)"
```

## Off Track
scale_fill_manual(values = alpha(c("blue", "red"), .3))

### Surface 
#### Temperature daily mean
"A" = "#a1dab4","B"="#253494"
```{r}
( plot1 <- ggplot(NULL, aes(x=date, y=airtemp)) + 
      geom_point(data = surfaceOff2, aes(color="A"), shape=21, alpha=.5) +
      geom_line(data = meanOffsurface, aes(color="B"), ) +
  labs(x="Date", y=tempLab, caption = "Off track") +
    scale_color_manual(values = c("A" = "#0868ac","B"="#7bccc4"), labels =c("A" ="2 minutes", "B"="Mean daily")) +
  theme_reg
  )
```

```{r}
( legend_temp <- ggplot(NULL, aes(x=date, y=airtemp)) + 
      geom_point(data = surfaceOff2, aes(color="A"), shape=21, alpha=.5) +
      geom_line(data = meanOffsurface, aes(color="B"), size=2) +
  labs(x="Date", y=tempLab) +
    scale_color_manual(values = c("A" = "#0868ac","B"="#7bccc4"), labels =c("A" ="2 minutes", "B"="Mean daily")) +
  theme_legend
  )
```
#### Mean RH
#99d8c9
#2ca25f
```{r}
( plot2 <- ggplot(NULL, aes(x=date, y=rh)) + 
      geom_point(data = surfaceOff2, aes(color="A"), shape=21, alpha=.5) +
      geom_line(data = meanOffsurface, aes(color="B")) +
  labs(x="Date", y=rhLab, caption = "Off track") +
    scale_color_manual(values = c("A" = "#99d8c9","B"="#2ca25f"), labels =c("A" ="2 minutes", "B"="Mean daily")) +
  theme_reg
  )
```
```{r}
( legend_rh <- ggplot(NULL, aes(x=date, y=rh)) + 
      geom_point(data = surfaceOff2, aes(color="A"), shape=21, alpha=.5) +
      geom_line(data = meanOffsurface, aes(color="B"), size=2) +
  labs(x="Date", y=rhLab, caption = "Off track") +
    scale_color_manual(values = c("A" = "#99d8c9","B"="#2ca25f"), labels =c("A" ="2 minutes", "B"="Mean daily")) +
  theme_legend
  )
```
### Subsurface 

#### VWC
```{r}
( plot3 <- ggplot() + 
      geom_line(data = meanOffsub, aes(x=date, y=vwc1, color="A")) +
      geom_line(data = meanOffsub, aes(x=date, y=vwc2, color="B")) +
      geom_line(data = meanOffsub, aes(x=date, y=vwc3, color="C")) +
      geom_line(data = meanOffsub, aes(x=date, y=vwc4, color="D")) +
  labs(x="Date", y=vwcUnits, caption = "Vertical profile off track") +
    scale_color_manual(values = c("A" = "#016c59","B"="#1c9099", "C"="#67a9cf", "D"="#bdc9e1"), labels =c("A" ="0 cm", "B"="10 cm", "C"="20 cm", "D"="30 cm")) +
  theme_reg
 )
```
 scale_color_manual(values = c("A" ="#fdae61","B" = "#ff6347", "C" = "#fee08b"), labels = c( "A" ="Tweedsmuir fire","B" = "Entiako fire", "C" = "Chelaslie fire" ), name = "Fire perimeters") +

```{r}
( legend_sub <- ggplot() + 
      geom_line(data = meanOffsub, aes(x=date, y=vwc1, color="A")) +
      geom_line(data = meanOffsub, aes(x=date, y=vwc2, color="B")) +
      geom_line(data = meanOffsub, aes(x=date, y=vwc3, color="C")) +
      geom_line(data = meanOffsub, aes(x=date, y=vwc4, color="D")) +
  labs(x="Date", y=vwcUnits, caption = "Vertical profile off track") +
    scale_color_manual(values = c("A" = "#016c59","B"="#1c9099", "C"="#67a9cf", "D"="#bdc9e1"), labels =c("A" ="0 cm", "B"="10 cm", "C"="20 cm", "D"="30 cm")) +
  theme_legend
 )
```
#### Temperature
```{r}
( plot4 <- ggplot() + 
      geom_line(data = meanOffsub, aes(x=date, y=temp1, color="A")) +
      geom_line(data = meanOffsub, aes(x=date, y=temp2, color="B")) +
      geom_line(data = meanOffsub, aes(x=date, y=temp3, color="C")) +
      geom_line(data = meanOffsub, aes(x=date, y=temp4, color="D")) +
  labs(x="Date", y=tempUnits, caption = "Vertical profile off track") +
     scale_color_manual(values = c("A" = "#016c59","B"="#1c9099", "C"="#67a9cf", "D"="#bdc9e1"), labels =c("A" ="0 cm", "B"="10 cm", "C"="20 cm", "D"="30 cm")) +
  theme_reg
 )
```

#### EC
```{r}
( plot5 <- ggplot() + 
      geom_line(data = meanOffsub, aes(x=date, y=ec1, color="A")) +
      geom_line(data = meanOffsub, aes(x=date, y=ec2, color="B")) +
      geom_line(data = meanOffsub, aes(x=date, y=ec3, color="C")) +
      geom_line(data = meanOffsub, aes(x=date, y=ec4, color="D")) +
  labs(x="Date", y=ecUnits, caption = "Vertical profile off track") +
     scale_color_manual(values = c("A" = "#016c59","B"="#1c9099", "C"="#67a9cf", "D"="#bdc9e1"), labels =c("A" ="0 cm", "B"="10 cm", "C"="20 cm", "D"="30 cm")) +
  theme_reg
 )
```

## On Track

### Surface 
#### Temperature mean daily
```{r}
( plot6 <- ggplot(NULL, aes(x=date, y=airtemp)) + 
      geom_point(data = surfaceOn2, aes(color="A"), shape=21, alpha=.5) +
      geom_line(data = meanOnsurface, aes(color="B")) +
  labs(x="Date", y=tempLab, caption = "On track") +
    scale_color_manual(values = c("A" = "#0868ac","B"="#7bccc4"), labels =c("A" ="2 minutes", "B"="Mean daily")) +
  theme_reg
  )
```

#### Mean RH
```{r}
( plot7 <- ggplot(NULL, aes(x=date, y=rh)) + 
      geom_point(data = surfaceOn2, aes(color="A"), shape=21, alpha=.5) +
      geom_line(data = meanOnsurface, aes(color="B")) +
  labs(x="Date", y=rhLab, caption = "On track") +
    scale_color_manual(values = c("A" = "#99d8c9","B"="#2ca25f"), labels =c("A" ="2 minutes", "B"="Mean daily")) +
  theme_reg
  )
```

### Subsurface 

#### VWC
```{r}
( plot8 <- ggplot() + 
      geom_line(data = meanOnsub, aes(x=date, y=vwc1, color="A")) +
      geom_line(data = meanOnsub, aes(x=date, y=vwc2, color="B")) +
      geom_line(data = meanOnsub, aes(x=date, y=vwc3, color="C")) +
      geom_line(data = meanOnsub, aes(x=date, y=vwc4, color="D")) +
  labs(x="Date", y=vwcUnits, caption = "Vertical profile on track") +
    scale_color_manual(values = c("A" = "#016c59","B"="#1c9099", "C"="#67a9cf", "D"="#bdc9e1"), labels =c("A" ="0 cm", "B"="10 cm", "C"="20 cm", "D"="30 cm")) +
  theme_reg
 )
```
 scale_color_manual(values = c("A" ="#fdae61","B" = "#ff6347", "C" = "#fee08b"), labels = c( "A" ="Tweedsmuir fire","B" = "Entiako fire", "C" = "Chelaslie fire" ), name = "Fire perimeters") +
  
#### Temperature
```{r}
( plot9 <- ggplot() + 
      geom_line(data = meanOnsub, aes(x=date, y=temp1, color="A")) +
      geom_line(data = meanOnsub, aes(x=date, y=temp2, color="B")) +
      geom_line(data = meanOnsub, aes(x=date, y=temp3, color="C")) +
      geom_line(data = meanOnsub, aes(x=date, y=temp4, color="D")) +
  labs(x="Date", y=tempUnits, caption = "Vertical profile on track") +
     scale_color_manual(values = c("A" = "#016c59","B"="#1c9099", "C"="#67a9cf", "D"="#bdc9e1"), labels =c("A" ="0 cm", "B"="10 cm", "C"="20 cm", "D"="30 cm")) +
  theme_reg
 )
```

#### EC
```{r}
( plot10 <- ggplot() + 
      geom_line(data = meanOnsub, aes(x=date, y=ec1, color="A")) +
      geom_line(data = meanOnsub, aes(x=date, y=ec2, color="B")) +
      geom_line(data = meanOnsub, aes(x=date, y=ec3, color="C")) +
      geom_line(data = meanOnsub, aes(x=date, y=ec4, color="D")) +
  labs(x="Date", y=ecUnits, caption = "Vertical profile on track") +
     scale_color_manual(values = c("A" = "#016c59","B"="#1c9099", "C"="#67a9cf", "D"="#bdc9e1"), labels =c("A" ="0 cm", "B"="10 cm", "C"="20 cm", "D"="30 cm")) +
  theme_reg
 )
```


# Combined plots
## Surface
```{r}
temp_leg = get_legend(legend_temp)
rh_leg = get_legend(legend_rh)
```

```{r}
combineLegend <- cowplot::plot_grid(
  temp_leg,
  rh_leg,
  ncol = 2)
```

```{r}
( g1 = cowplot::plot_grid(plot1,plot2, plot6, plot7, ncol=2, labels = "auto")
  )
```

```{r}
( g1.1 = cowplot::plot_grid(g1, combineLegend, ncol = 1, rel_heights = c(1, .05))
)
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/SurfaceMeasures.tiff", plot = g1.1, width = 6, height =5, units = c("in"), dpi=600, bg = "white" )
```

## Subsurface

```{r}
sub_leg = get_legend(legend_sub)
```

```{r fig.height=7, fig.width=6}
( g2 = cowplot::plot_grid(plot3, plot8, plot4,plot9, plot5, plot10, ncol=2, labels = "auto")
  )
```

```{r}
( g2.1 = cowplot::plot_grid(g2, sub_leg, ncol = 1, rel_heights = c(1, .05))
)
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/VerticalProfileMeasures.tiff", plot = g2.1, width = 6, height =7, units = c("in"), dpi=600, bg = "white" )
```